Plot Figures for McDuffie et al., 2023 (those generated in R)

### 2023-05-12 analysis/Manuscript/Paper_RFigures.Rmd
Minor updates to rft output and figure script

Results <- file.path('Results')
globalresults <-
  read_csv(file.path(inputs,"npd_global_damage_transformation_woutCessation.csv"),
           col_types = cols())
Results2 <- file.path(rft_inputs,'npd_global_rff_means_NOx_1_MMM.csv')
rft_results <- read_csv(Results2, col_types = cols())
nox_results1 <- file.path(rft_inputs,'npd_global_rff_means_NOx_1_MMM.csv')
nox_results1 <- read_csv(nox_results1, col_types = cols())%>%
  mutate(NOx = '1')
nox_results5 <- file.path(rft_inputs, 'npd_global_rff_means_NOx_0.5_MMM.csv')
nox_results5 <- read_csv(nox_results5, col_types = cols())%>%
  mutate(NOx = '0.5')
nox_results15 <- file.path(rft_inputs, 'npd_global_rff_means_NOx_1.5_MMM.csv')
nox_results15 <- read_csv(nox_results15, col_types = cols()) %>%
  mutate(NOx = '1.5')
nox_total_results <- rbind(nox_results1,nox_results5,nox_results15)

>>>>

Results <- file.path('Results')
globalresults <-
  read_csv(file.path(inputs,"npd_global_damage_transformation_woutCessation.csv"),
           col_types = cols())
Results2 <- file.path(rft_inputs,'npd_global_rff_means_NOx_1_MMM.csv')
rft_results <- read_csv(Results2, col_types = cols())
nox_results1 <- file.path(rft_inputs,'npd_global_means_NOx_1_MMM.csv')
nox_results1 <- read_csv(nox_results1, col_types = cols())%>%
  mutate(NOx = '1')
nox_results5 <- file.path(rft_inputs, 'npd_global_means_NOx_0.5_MMM.csv')
nox_results5 <- read_csv(nox_results5, col_types = cols())%>%
  mutate(NOx = '0.5')
nox_results15 <- file.path(rft_inputs, 'npd_global_means_NOx_1.5_MMM.csv')
nox_results15 <- read_csv(nox_results15, col_types = cols()) %>%
  mutate(NOx = '1.5')
nox_total_results <- rbind(nox_results1,nox_results5,nox_results15)
